\ttitle

### 2016-02-19 Chapters/BodyComp.tex
\caption* in Body comp

	\caption[Selection of components of body composition from CT images using GIMP.]
	{Selection of components of body composition from CT images using the GNU Image Manipulation Program (GIMP).\\ The total cross-sectional area was selected by first selecting the empty space outside the image followed by inverting this selection as depicted in (A). The 'Fuzzy Select' tool was then used to select individual body composition components with visual confirmation using the 'layer selection' tool. This is shown in B, C and D. The selected area has been removed for representation purposes. The insets in each image confirm the area selected.}
	\label{fig:bc_ct_gimp}
\end{figure}

@@

\begin{figure}[htb]
	\centering
	\includegraphics[width=0.8\textwidth]{Figures/bc_gender_bmi_pie}
	\caption[Differences in body composition according to sex and body mass index.]
	{Differences in body composition according to sex and body mass index.
		\\Body composition differed significantly between men and women and with increasing body mass index (BMI). The proportion of skeletal muscle area decreased with increasing BMI in both sexes but there was a larger decrease in women than men. Visceral adipose tissue contributed more to weight in obese men than subcutaneous adipose tissue while the opposite was true in women.}
	\label{fig:bc_gender_bmi}
\end{figure}

@@

\begin{figure}[htb]
	\centering
	\begin{subfigure}[b]{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Figures/bc_scatter_atLoad_skeletal}
		\caption{Anaerobic Threshold}
		\label{fig:bc_at_load_vs_sm}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Figures/bc_scatter_pkLoad_skeletal}
		\caption{Peak Exercise}
		\label{fig:bc_pk_load_vs_sm}
	\end{subfigure}
	\caption[Correlation between exercise load and skeletal muscle area.]
	{Correlation between exercise load and skeletal muscle area.
		\\ Scatter plots A and B show a positive correlation between exercise load achieved and skeletal muscle area both at anaerobic threshold ($p < 0.001$) and peak exercise ($p < 0.001$) respectively.}	
	\label{fig:bc_load_vs_sm}

@@

%----------------------------------------------------------------------------------------------
% Correlation between body composition and $\dot{V}_{O_2}$AT before and after correction for total body weight.
\begin{figure}[htb]
	\centering
	\begin{subfigure}[b]{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Figures/bc_scatter_VO2_skeletal}
		\caption{$\dot{V}_{O_2}$AT vs. 
Skeletal Muscle}
		\label{fig:bc_scatter_VO2_skeletal}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Figures/bc_scatter_VO2_TAT}
		\caption{$\dot{V}_{O_2}$AT vs. 
Total Adipose Tissue}
		\label{fig:bc_scatter_VO2_TAT}
	\end{subfigure}
	\caption[Correlation between body composition and $\dot{V}_{O_2}$AT before and after correction for total body weight.]
	{Correlation between body composition and $\dot{V}_{O_2}$AT before and after correction for total body weight.
	\\ Scatter-plots were generated comparing absolute $\dot{V}_{O_2}$ (litres/minute, solid lines) and $\dot{V}_{O_2}$ normalised for total body weight (corrected $\dot{V}_{O_2}$, ml/kg/min, dotted lines) against skeletal muscle area (A) and total adipose tissue area (B). The solid line in A shows a positive correlation between absolute $\dot{V}_{O_2}$ and skeletal muscle area ($p<0.001$) while in B it shows no correlation with total adipose tissue as expected of exercise physiology. However, normalisation of $\dot{V}_{O_2}$ using total body weight results in a 'spurious' negative correlation with total adipose tisue area as depicted by the dotted line in B ($p<0.001$). This indicates that patients with high body mass index and excess adipose tissue will have low corrected $\dot{V}_{O_2}$, the value that is commonly used in clinical practice.}	
	\label{fig:bc_scatter_VO2_bodycomp_reversal}
\end{figure}
%----------------------------------------------------------------------------------------------

@@

%----------------------------------------------------------------------------------------------
% Correlation between body composition and $\dot{V}_{O_2}$AT before and after correction for total body weight.
\begin{figure}[htb]
	\centering
	\begin{subfigure}[b]{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Figures/bc_scatter_VO2_skeletal_elbm}
		\caption{$\dot{V}_{O_2}$AT vs. 
Skeletal Muscle}
		\label{fig:bc_scatter_VO2_skeletal_elbm}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Figures/bc_scatter_VO2_TAT_elbm}
		\caption{$\dot{V}_{O_2}$AT vs. 
Total Adipose Tissue}
		\label{fig:bc_scatter_VO2_TAT_elbm}
	\end{subfigure}
	\caption[Correlation between body composition and $\dot{V}_{O_2}$AT corrected for total body weight and estimated lean body mass.]
	{Correlation between body composition and $\dot{V}_{O_2}$AT corrected for total body weight and estimated lean body mass.
	\\ Fig. A shows that there is little difference in the relationship between skeletal muscle area and $\dot{V}_{O_2}$ corrected using either total body weight or estimated lean body mass. However, while $\dot{V}_{O_2}$ corrected for total body weight had a 'spurious' negative correlation with total adipose tissue area (solid line in B), this 'spurious' relationship was no longer present when $\dot{V}_{O_2}$ was normalised using estimated lean body mass (dotted line in B).}
	\label{fig:bc_scatter_VO2_bodycomp_elbm}
\end{figure}
%----------------------------------------------------------------------------------------------

>>>>

	\caption{Selection of components of body composition from CT images using GIMP.}
	\caption*{The total cross-sectional area was selected by first selecting the empty space outside the image followed by inverting this selection as depicted in (A). The 'Fuzzy Select' tool was then used to select individual body composition components with visual confirmation using the 'layer selection' tool. This is shown in B, C and D. The selected area has been removed for representation purposes. The insets in each image confirm the area selected.}
	\label{fig:bc_ct_gimp}
\end{figure}

@@

\begin{figure}[htb]
	\centering
	\includegraphics[width=0.8\textwidth]{Figures/bc_gender_bmi_pie}
	\caption{Differences in body composition according to sex and BMI.}
	\caption*{Body composition differed significantly between men and women and with increasing body mass index (BMI). The proportion of skeletal muscle area decreased with increasing BMI in both sexes but there was a larger decrease in women than men. Visceral adipose tissue contributed more to weight in obese men than subcutaneous adipose tissue while the opposite was true in women.}
	\label{fig:bc_gender_bmi}
\end{figure}

@@

\begin{figure}[htb]
	\centering
	\begin{subfigure}[b]{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Figures/bc_scatter_atLoad_skeletal}
		\caption{Anaerobic Threshold}
		\label{fig:bc_at_load_vs_sm}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Figures/bc_scatter_pkLoad_skeletal}
		\caption{Peak Exercise}
		\label{fig:bc_pk_load_vs_sm}
	\end{subfigure}
	\caption{Correlation between exercise load and skeletal muscle area.}
	\caption*{Scatter plots A and B show a positive correlation between exercise load achieved and skeletal muscle area both at anaerobic threshold ($p < 0.001$) and peak exercise ($p < 0.001$) respectively.}	
	\label{fig:bc_load_vs_sm}

@@

%----------------------------------------------------------------------------------------------
% Correlation between body composition and $\dot{V}_{O_2}$AT before and after correction for total body weight.
\begin{figure}[htb]
	\centering
	\begin{subfigure}[b]{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Figures/bc_scatter_VO2_skeletal}
		\caption{$\dot{V}_{O_2}$AT vs. 
Skeletal Muscle}
		\label{fig:bc_scatter_VO2_skeletal}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Figures/bc_scatter_VO2_TAT}
		\caption{$\dot{V}_{O_2}$AT vs. Total Adipose Tissue}
		\label{fig:bc_scatter_VO2_TAT}
	\end{subfigure}
	\caption{Correlation between body composition and $\dot{V}_{O_2}$AT before and after correction for total body weight.}
	\caption*{%Scatter-plots were generated comparing absolute $\dot{V}_{O_2}$ (litres/minute, solid lines) and $\dot{V}_{O_2}$ normalised for total body weight (corrected $\dot{V}_{O_2}$, ml/kg/min, dotted lines) against skeletal muscle area (A) and total adipose tissue area (B).
	 The solid line in A shows a positive correlation between absolute $\dot{V}_{O_2}$ and skeletal muscle area ($p<0.001$) while in B it shows no correlation with total adipose tissue as expected of exercise physiology. However, normalisation of $\dot{V}_{O_2}$ using total body weight results in a 'spurious' negative correlation with total adipose tisue area as depicted by the dotted line in B ($p<0.001$). This indicates that patients with high body mass index and excess adipose tissue will have low corrected $\dot{V}_{O_2}$, the value that is commonly used in clinical practice.}	
	\label{fig:bc_scatter_VO2_bodycomp_reversal}
\end{figure}
%----------------------------------------------------------------------------------------------

@@

%----------------------------------------------------------------------------------------------
% Correlation between body composition and $\dot{V}_{O_2}$AT before and after correction for total body weight.
\begin{figure}[htb]
	\centering
	\begin{subfigure}[b]{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Figures/bc_scatter_VO2_skeletal_elbm}
		\caption{$\dot{V}_{O_2}$AT vs. 
Skeletal Muscle}
		\label{fig:bc_scatter_VO2_skeletal_elbm}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Figures/bc_scatter_VO2_TAT_elbm}
		\caption{$\dot{V}_{O_2}$AT vs. 
Total Adipose Tissue}
		\label{fig:bc_scatter_VO2_TAT_elbm}
	\end{subfigure}
	\caption{Correlation between body composition and $\dot{V}_{O_2}$AT corrected for total body weight and estimated lean body mass.}
	\caption*{Fig. A shows that there is little difference in the relationship between skeletal muscle area and $\dot{V}_{O_2}$ corrected using either total body weight or estimated lean body mass. However, while $\dot{V}_{O_2}$ corrected for total body weight had a 'spurious' negative correlation with total adipose tissue area (solid line in B), this 'spurious' relationship was no longer present when $\dot{V}_{O_2}$ was normalised using estimated lean body mass (dotted line in B).}
	\label{fig:bc_scatter_VO2_bodycomp_elbm}
\end{figure}
%----------------------------------------------------------------------------------------------

### 2016-02-19 Tables/bc_at_new_indices.tex
\caption* in Body comp

		Variable              	& $\rho$ &\textit{p}& $\rho$ &\textit{p}& $\rho$ &\textit{p}& $\rho$ &\textit{p}& $\rho$ &\textit{p}& $\rho$ &\textit{p} \\ \hline
		Subcut. fat (cm$^2$)     & 0.191  &  0.089   & -0.326 &  0.003   & 0.169  &  0.132   & -0.217 &  0.051   & 0.018  &  0.872   & -0.041 & 0.716 \\
		Visceral fat (cm$^2$)    & 0.184  &  0.103   & -0.365 &  0.001   & 0.154  &  0.168   & -0.279 &  0.012   & -0.065 &  0.563   & -0.108 & 0.339\\
		Total fat (cm$^2$)       & 0.231  &  0.038   & -0.400 & $<$0.001 & 0.191  &  0.088   & -0.286 &  0.010   & -0.021 &  0.851   & -0.082 & 0.466\\
		Skeletal Muscle (cm$^2$) & 0.463  & $<$0.001 & -0.078 &  0.487   & 0.329  &  0.003   & 0.105  &  0.353   & -0.429 & $<$0.001 & 0.133 & 0.237 \\
		Height (cm)               & 0.446  & $<$0.001 & 0.019  &  0.870   & 0.001  &  0.993   & 0.475  & $<$0.001 & 0.105  &  0.350   & 0.019 & 0.865\\
		Weight (kg)               & 0.545  & $<$0.001 & -0.302 &  0.006   & 0.358  &  0.001   & -0.043 &  0.703   & 0.001  &  0.995   & 0.033 & 0.770\\
		Body Mass Index (kg/m$^2$)      & 0.357  &  0.001   & -0.363 &  0.001   & 0.425  & $<$0.001 & -0.345 &  0.002   & -0.059 &  0.603   & 0.035 & 0.756\\ \hline
		\multicolumn{11}{l}{$\rho$ - Pearson's partial correlation adjusted for sex.}
	\end{tabular}
	\medskip
	\begin{flushleft}
		$\dot{V}_{O_2}$AT normalised using different measures of body habitus (including weight, square of height, body mass index, skeletal muscle area and estimated lean body mass) was compared to body composition as well as weight, height and BMI in an exploratory analysis. Scaling $\dot{V}_{O_2}$AT using estimated lean body mass was the only method studied that did not result in any 'spurious' correlations with body composition or body habitus. This is also depicted in Fig. \ref{fig:bc_scatter_VO2_bodycomp_elbm} on page \pageref{fig:bc_scatter_VO2_bodycomp_elbm}.
	\end{flushleft}
\end{sidewaystable}

>>>>

		Variable              	& $\rho$ &\textit{p}& $\rho$ &\textit{p}& $\rho$ &\textit{p}& $\rho$ &\textit{p}& $\rho$ &\textit{p}& $\rho$ &\textit{p} \\ \hline
		Subcut. fat (cm$^2$)     & 0.191  &  0.089   & -0.326 &  0.003   & 0.169  &  0.132   & -0.217 &  0.051   & 0.018  &  0.872   & -0.041 & 0.716 \\
		Visceral fat (cm$^2$)    & 0.184  &  0.103   & -0.365 &  0.001   & 0.154  &  0.168   & -0.279 &  0.012   & -0.065 &  0.563   & -0.108 & 0.339\\
		Total fat (cm$^2$)       & 0.231  &  0.038   & -0.400 & $<$0.001 & 0.191  &  0.088   & -0.286 &  0.010   & -0.021 &  0.851   & -0.082 & 0.466\\
		Skeletal Muscle (cm$^2$) & 0.463  & $<$0.001 & -0.078 &  0.487   & 0.329  &  0.003   & 0.105  &  0.353   & -0.429 & $<$0.001 & 0.133 & 0.237 \\
		Height (cm)               & 0.446  & $<$0.001 & 0.019  &  0.870   & 0.001  &  0.993   & 0.475  & $<$0.001 & 0.105  &  0.350   & 0.019 & 0.865\\
		Weight (kg)               & 0.545  & $<$0.001 & -0.302 &  0.006   & 0.358  &  0.001   & -0.043 &  0.703   & 0.001  &  0.995   & 0.033 & 0.770\\
		Body Mass Index (kg/m$^2$)      & 0.357  &  0.001   & -0.363 &  0.001   & 0.425  & $<$0.001 & -0.345 &  0.002   & -0.059 &  0.603   & 0.035 & 0.756\\ \hline
		\multicolumn{11}{l}{$\rho$ - Pearson's partial correlation adjusted for sex.}
	\end{tabular}
	\medskip
	\caption*{$\dot{V}_{O_2}$AT normalised using different measures of body habitus (including weight, square of height, body mass index, skeletal muscle area and estimated lean body mass) was compared to body composition as well as weight, height and BMI in an exploratory analysis. Scaling $\dot{V}_{O_2}$AT using estimated lean body mass was the only method studied that did not result in any 'spurious' correlations with body composition or body habitus. This is also depicted in Fig. \ref{fig:bc_scatter_VO2_bodycomp_elbm} on page \pageref{fig:bc_scatter_VO2_bodycomp_elbm}.}
\end{sidewaystable}
